%-------------------------
% Resume in Latex
% Author : Islam Ibrahim
% Based off of: https://github.com/islamibr/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[backend=biber, style=numeric, labelnumber=false]{biblatex}
\addbibresource{Publications.bib}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{amsmath}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\normalsize\bfseries
}{}{0em}{}
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%------------------------
\defbibenvironment{bibliography}
  {\list%
     {\printtext[labelnumberwidth]{%
        \printfield{prefixnumber}%
        \printfield{labelnumber}}}%
     {\setlength{\labelwidth}{\labelnumberwidth}%
      \setlength{\leftmargin}{\labelwidth}%
      \setlength{\labelsep}{5pt}
      \addtolength{\leftmargin}{\labelsep}%
      \setlength{\itemsep}{\bibitemsep}%
      \setlength{\parsep}{\bibparsep}}%
      \renewcommand*{\makelabel}[1]{\smash{\raisebox{0.5ex}{\tiny\textbullet}}}}
  {\endlist}
  {\item}
%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2}\vspace{-3pt} \\
      \text{\footnotesize#3} & \text{\footnotesize #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-3pt} \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{\footnotesize#1} & \text{\small #2} \vspace{-3pt}\\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \Huge Islam Ibrahim Abdelal} \\ \vspace{1pt}
    Alexandria, Egypt \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +20-120-460-9271 ~ \href{mailto:eslam.ibrahim2026@alexu.edu.eg}{\raisebox{-0.2\height}\faEnvelope\  \underline{es-eslam.ibrahim2026@alexu.edu.eg}} ~ 
    \href{https://linkedin.com/in/islamibr29}{\raisebox{-0.2\height}\faLinkedin\ \underline{in/islamibr29}}  ~
    \href{https://github.com/islamibr}{\raisebox{-0.2\height}\faGithub\ \underline{@islamibr}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\vspace{-10pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading 
      {Alexandria University}{Sep. 2021 -- May 2026}
      {BEng, Electrical Engineering, Electronics Major \,\,\,\ \textbf{CGPA:}  3.51}{Alexandria, Egypt}
        \resumeItemListStart
        \resumeItem{Key Courses: Circuits Analysis, Solid State Devices, Electronics I, Electronics II, C Programming}
        \resumeItem{Key Skills: VHDL, Quartus, ModelSim, LabVIEW, \LaTeX, Python, C, Proteus, ElecNet, AutoCAD, Dialux, STK, PSpice, Multisim, TinkerCAD.}
        \resumeItem{Key Projects: \href{https://github.com/islamibr/MIM_capacitor_and_magnetic_buzzer}{MIM Capacitor and Magnetic Buzzer}, \href{https://github.com/islamibr/serial_data_receiver}{Serial Data Receiver}, \href{https://github.com/islamibr/4-bit_up_counter_with_parallel_load}{4-bit Up Counter with Parallel Load}, \href{https://www.tinkercad.com/things/3uQqwDWqwkg-avometermultimeter}{AVOmeter/Multimeter}, \href{https://github.com/islamibr/k-map_calculator}{K-Map Calculator}, \href{https://github.com/islamibr/hex_keypad}{Hex Keypad}.}
         
      \resumeItemListEnd \vspace{-5pt}
  \resumeSubHeadingListEnd

\vspace{-10pt}
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  \begin{comment}
     \vspace{-5pt}
    \subsection{Work Experience}
    \vspace{-15pt}
    \resumeSubheading
      {Startup, Inc}{May 2019 -- August 2019}
      {Front End Developer Intern}{City, State}
      \resumeItemListStart
        \resumeItem{Assisted in development of the front end of a mobile application for iOS/Android using Dart and the Flutter framework.}
        \resumeItem{Worked with Google Firebase to manage user inputted data across multiple platforms including web and mobile apps.}
        \resumeItem{Collaborated with team members using version control systems such as Git to organize modifications and assign tasks.}
        \resumeItem{Utilized Android Studio as a development environment in order to visualize the application in both iOS and Android.} \end{comment}
        \vspace{-3pt}
    \subsection{Research Experience}
    \vspace{-5pt}
    \resumeSubheading
      {Alexandria University}{Jun. 2023 -- Present}
      {Undergraduate Research Assistant}{Alexandria, Egypt}
      \resumeItemListStart
        \resumeItem{Under Supervision of Dr. Ishac Kandas and Dr. Eman Elzahaby, Working on Applied Optics Especially Photonic Integrated Circuits (PICs) and Optical Neural Networks (ONNs).}
        \resumeItem{Key Skills: Lumerical, COMSOL, MATLAB, Python, \LaTeX, EdrawMax, Illustrator, Visio, Blender, Paint 3D, Mendeley, \textsc{Bib}\TeX.}
      \resumeItemListEnd
      \begin{comment}
     \vspace{-5pt}
    \subsection{Training and Internships}
    \vspace{-15pt}
    \resumeSubheading
      {Startup, Inc}{May 2019 -- August 2019}
      {Front End Developer Intern}{City, State}
      \resumeItemListStart
        \resumeItem{Assisted in development of the front end of a mobile application for iOS/Android using Dart and the Flutter framework.}
        \resumeItem{Worked with Google Firebase to manage user inputted data across multiple platforms including web and mobile apps.}
        \resumeItem{Collaborated with team members using version control systems such as Git to organize modifications and assign tasks.}
        \resumeItem{Utilized Android Studio as a development environment in order to visualize the application in both iOS and Android.} \end{comment}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------Publications-----------
\section{Publications}
    \nocite{*}
        \resumeSubHeadingListStart
         \bibliographystyle{IEEEtran}
%        \subsection{Journal Articles} \vspace{-10pt}
 %       \printbibliography[heading={none}, type=article] \vspace{-20pt}
        % \subsection{Conference Proceedings} \vspace{-10pt}
       % \printbibliography[heading={none},type=proceeding]
       \vspace{-3pt} \subsection{Unpublished Articles} \vspace{-10pt}
        \printbibliography[heading={none},type=unpublished]
        \resumeSubHeadingListEnd

\vspace{-25pt}
%-----------PROJECTS-----------
\section{Projects}
         \subsection{Simulation} \vspace{-20pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://www.tinkercad.com/things/gVrKAFyUruq-smartplantcaresystemwithautowateringrefilling}{Smart Plant Care System}} $|$ \emph{Arduino, ThinkerCAD}}{Aug 2022} 
           \resumeItem{I did the \textbf{Assessment} of automating care with soil sensors, buttons, and Arduino Uno for efficient watering control.} \vspace{-15pt}
          \resumeProjectHeading 
          {\textbf{\href{https://www.tinkercad.com/things/esnvsztXcxI-smartgreenhousemonitoringandcontrolsystem}{Smart Greenhouse System}} $|$ \emph{Arduino, ThinkerCAD, UART}}{Aug 2022}
          \resumeItem{I did the \textbf{Assessment} of three subsystems: Sensing, Master and Action, Soil - Using Arduino Uno for seamless control.} 
    \resumeSubHeadingListEnd \vspace{-15pt}
    \subsection{Programming} \vspace{-20pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/islamibr/robot_rental_system}{Robot Rental System}} $|$ \emph{C++, OOP}}{Aug 2022}
          \resumeItem{I did the \textbf{Assessment} of command-line app for managing robot rentals, user info, and seamless rental processes.}
    \resumeSubHeadingListEnd \vspace{-15pt}
    \subsection{HDLs (RTL)} \vspace{-20pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://github.com/islamibr/8x8_seq_mult}{8x8 Bit Sequential Multiplier}} $|$ \emph{Verilog, Vivado, QuestaSim}}{Aug 2023}
          \resumeItem{I did the \textbf{Controller} Part of streamlined 8-bit operand multiplication, yielding a 16-bit product with multi-cycle computation.}
    \resumeSubHeadingListEnd
\vspace{-30pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{center}

\renewcommand{\arraystretch}{-20}
\begin{tabularx}{\textwidth}{p{0.33\textwidth}p{0.33\textwidth}p{0.33\textwidth}}
    \textbf{Simulation and Modeling} & \textbf{Programming and Scripting} & \textbf{Description and Implementation} \\ \vspace{-10}
    \small
    \begin{itemize}[leftmargin=0, label={}, itemsep=0, parsep=0pt]
        \item \textbf{Circuits}: \text{Virtuoso}
        \item \textbf{Devices}: \text{TCAD}
        \item \textbf{PCBs}: \text{Proteus, Allegro}
        \item \textbf{ASICs}: \text{QuestaSim, ModelSim}
    \end{itemize}
    &
    \small  \vspace{-10}
    \begin{itemize}[leftmargin=0, label={}, itemsep=0, parsep=0pt]
        \item \textbf{Programming}: \text{C/C++, MATLAB,} \newline \text{Python}
        \item \textbf{Scripting}: \text{\LaTeX}
    \end{itemize}
    &
    \small  \vspace{-10}
    \begin{itemize}[leftmargin=0, label={}, itemsep=0, parsep=0pt]
        \item \textbf{HDLs (RTL)}: \text{VHDL, Verilog}
        \item \textbf{FPGAs}: \text{Quartus, Vivado}
    \end{itemize}
    \\
\end{tabularx}
\end{center}

\vspace{-30pt}
\section{Languages}
English: B2, Arabic: Native

\vspace{-10pt}
%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
    \resumeSubheading
      {Education Clinic}{Aug. 2021 -- Sep. 2023}
      {General Coordinator}{Remote}
      \resumeItemListStart \vspace{-5pt}
        \resumeItem{Successfully transitioned from Jr. Graphic Designer to General Coordinator within a year, strategically bypassing the Team Lead role, under the guidance of Dr. Ramzy Abdelaziz.} \vspace{-5pt}
        \resumeItem{Boosted program completion rates by 20\% through effective management of educational initiatives for a non-profit organization impacting 100,000+ students. Also contributed to a 30\% surge in program participation rates.} \vspace{-5pt}
        \resumeItem{Key skills: Strategic Management, General Management, Project Management, Agile Management, Marketing, Creative Suite, Canva, Visme, Figma,  Google Workspace, Office.}
      \resumeItemListEnd \newpage
    \resumeSubheading
      {Hult Prize Egypt}{Sep. 2022 -- Jan. 2023}
      {Corporate Relations Specialist}{Remote}
      \resumeItemListStart \vspace{-5pt}
        \resumeItem{Devised and executed effective corporate relations strategies, identifying and securing potential IEEE SAC and AIESEC partnerships and EG Bank sponsorship, resulting in a 50\% increase in overall partnerships and sponsorships.} \vspace{-5pt}
        \resumeItem{Collaborated closely with the Hult Prize Egypt team and global network, ensuring seamless alignment with the organization's goals and objectives and contributing to the growth of a community of changemakers, resulting in a 3000 changemaker increase in community engagement and impact.} \vspace{-5pt}
        \resumeItem{Key skills: Event Management, Crisis Management, Public Relations Campaigns, Strategic Partnerships, Sponsorships and Fundraising.}
      \resumeItemListEnd
        
    \resumeSubHeadingListEnd
    \vspace{-25pt}
\section{Achievements}
\renewcommand{\arraystretch}{-20}
\begin{tabularx}{\textwidth}{p{0.5\textwidth}p{0.5\textwidth}}
    \textbf{Recognition and Accomplishments} & \textbf{Licenses and Certifications}  \\ \vspace{-10}
    \small
    \begin{itemize}[leftmargin=0, label={}, itemsep=0, parsep=0pt]
        \item ICT Competition National Finalist by Huawei Academy
        \item Young Egyptian Influencer by Magazine, 30.30
        \item Global Nominee by NASA Space Apps Challenge
        \item GSEC Top Achiever by Egyptian Ministry of Education
    \end{itemize}
    & \begin{comment}
        
    \end{comment}
    \small  \vspace{-10}
    \begin{itemize}[leftmargin=0, label={}, itemsep=0, parsep=0pt]
        \item \textbf{EF SET} Score: 61-70/C1 · Mar 2021
       %  \item MATLAB for Engineers by Couresera
    \end{itemize}
\end{tabularx}
\vspace{-25pt}
% \section{Miscellaneous}

%\vspace{-10pt}
\section{References}
\begin{multicols}{2}
  \textbf{Dr. Yasser Hassan} \vspace{-3pt}\\ 
  Ex-fellow, Oxford University \vspace{-3pt}\\
  Ass. Prof., Qatar University \vspace{-3pt}\\
  Case: Education Clinic Founder \vspace{-3pt}\\
  \faEnvelope \ \href{mailto:yhassan@qu.edu.qa}{yhassan@qu.edu.qa}

  \columnbreak

  \textbf{Dr. Ishac Kandas} \vspace{-3pt}\\
  PhD, Virginia Tech \vspace{-3pt}\\
  Ass. Prof., Alexandria University \vspace{-3pt}\\
  Case: Research Supervisor \vspace{-3pt}\\
  \faEnvelope \ \href{mailto:ishac@vt.edu}{ishac@vt.edu}

\begin{comment}
    \columnbreak

  \textbf{Dr. X}\\
  PhD, McMaster University\\
  Ass. Professor, Alexandria University\\
  Case: Graduation Project Supervisor\\
  \faEnvelope \ \href{mailto:x@alexu.edu.eg}{x@alexu.edu.eg}
  
\end{comment}
  
\end{multicols}

\end{document}
